On the performance of the MAC model

### 2018-11-01 2018_nips_vigil/appendix.tex
Appendix A - cleaning

Along with CLEVR, the authors~\cite{johnson2017clevr} introduced  CLEVR-CoGenT (Compositional Generalization Test, CoGenT in short), with a goal of testing how well the models can learn and generalize compositional concepts.
This dataset is synthesized in the same way as CLEVR, but contains two conditions.
As shown in \tableref{tab:cogent_conditions}, in Condition A all cubes are gray, blue, brown, or yellow, whereas all cylinders are red, green, purple, or cyan; in Condition B cubes and cylinders swap color palettes.
Both conditions contain spheres of all colors.
CoGenT thus indicates how a model answers CLEVR questions: by memorizing combinations of traits or by learning disentangled or general representations.
The CoGenT dataset contains:
\begin{itemize}
\item	A training set of 70,000 images and 699,960 questions in Condition A,
\item	A validation set of 15,000 images and 150,000 questions in Condition A,
\item	A validation set of 15,000 images and 149,991 questions in Condition B,
\item	A test set of 15,000 images and 149,980 questions in Condition B,
\item	A test set of 15,000 images and 149,992 questions in Condition B,
\item	Answers, scene graphs and functional programs for all training and validation images and questions.
\end{itemize}

>>>>

Along with CLEVR, the authors~\cite{johnson2017clevr} introduced  CLEVR-CoGenT (Compositional Generalization Test, CoGenT in short), with a goal of evaluating how well the models can generalize, learn relations and compositional concepts.
This dataset is generated in the same way as CLEVR with two additional conditions.
As shown in \tableref{tab:cogent_conditions}, in Condition A all cubes are gray, blue, brown, or yellow, whereas all cylinders are red, green, purple, or cyan; in Condition B cubes and cylinders swap color palettes.
For both conditions spheres can be any colors.

The CoGenT task give a sense on how the model solve CLEVR question. Is the model learning combination of attributes or general representations?

The CoGenT dataset contains:
\begin{itemize}
\item	A training set of 70,000 images and 699,960 questions in Condition A,
\item	A validation set of 15,000 images and 150,000 questions in Condition A,
\item	A validation set of 15,000 images and 149,991 questions in Condition B,
\item	A test set of 15,000 images and 149,980 questions in Condition B,
\item	A test set of 15,000 images and 149,992 questions in Condition B,
\item	Answers, scene graphs and functional programs for all training and validation images and questions.
\end{itemize}
